PhD Thesis

### 2016-12-02 thesis-main.tex
Prepare integration: fix conflicts with polytable
Integrate lhs2tex support
lhs2tex uses polytable, hence the previous commit was needed.
Fully integrate
* newlhs: remove symlinks and copy-pasted code to compile separately
* all lhs2TeX files need the same basic support (e.g., both must use
  polycode.fmt in this case).
* update Makefile for the new compilation workflow (adapting the one
  from newlhs/).
Move AOSD13 acknowledgments

\documentclass{book}
\usepackage{natbib}
\usepackage{comment}
\bibliographystyle{abbrvnat}
\input{packages}
\input{macros}

@@

\newcommand{\co}[1]{\code{#1}} %Adaptation between different interfaces
\chapter{Incrementalizing simply-typed \TitleLambda{}-calculus}
\input{pldi14/agda}

@@

\bibliography{Bibs/DB,Bibs/ProgLang,Bibs/SoftEng,Bibs/own}
\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

\documentclass{book}
\usepackage{mylhs2tex}
\usepackage{natbib}
\usepackage{comment}
\bibliographystyle{abbrvnat}
\input{packages}
\input{macros}

@@

\newcommand{\co}[1]{\code{#1}} %Adaptation between different interfaces

\input{newlhs/new}

\chapter{Incrementalizing simply-typed \TitleLambda{}-calculus}
\input{pldi14/agda}

@@

\bibliography{Bibs/DB,Bibs/ProgLang,Bibs/SoftEng,Bibs/own}
\chapter*{Acknowledgments}
% From AOSD13
I thank Sebastian Erdweg for helpful discussions on
this project, Katharina Haselhorst for help
implementing the code generator, and the anonymous reviewers, Jacques Carette and Karl Klose
for their helpful comments on this chapter.
This work is supported in part by the European Research Council, grant \#203099 ``ScalPL''.

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
